---
title: |
  | \vspace{6cm} ST505: Project
author: "Apostolos Stamenos"
date: '2022-11-12'
header-includes:
  - \usepackage{float}
  - \usepackage{indentfirst}
  - \usepackage{caption}
  - \floatplacement{figure}{H}
geometry: "left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm"
linestretch: 1.2
indent: true
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

\newpage

# Introduction


# Data Collection Protocol

The data was collected to help the Department of Health and Human Services, the Department of Education, and the White House assess how schools were operating during the COVID-19 pandemic (___, ). For the purposes of this assessment, we used the following definitions for school learning modalities:

* In-Person:
* Remote:
* Hybrid:

The main dataset of interest contains information about approximately $14,500$ K-12 public school and independent charter school districts in the U.S. The dataset contains information about the number of schools within each school district and the total number of students throughout the district. Some school districts contain a single school, whereas others contain multiple schools.

Based on the National Center for Education Statistics (NCES, 20xx), throughout the country, there are more than $17,000$ school districts that meet this definition. Clearly, the school districts included in the learning modalities dataset constitute just a subset of all public and independent charter school districts.


The data is an observational study, since there are no random treatment assignments.

Potential confounders: ventilation and air flow, physical size of school building (i.e., are students able to sit far enough apart), 

In addition to the learning modality dataset, I also imported state-level vaccination data from (), case and death data from (), and population estimate data from ___.

# The Statistical Analysis



Missingness may be happening at random, or there might be a systematic reason for the missing data. For example, districts that are not operating fully in person may be less likely to respond, in which case there would be underreporting of "remote" and "hybrid" learning modalities.

Unperceived characteristics in different Census regions (e.g., political ideology, attitude toward public health and COVID restrictions, differences in local education laws, etc).

# Conclusion


\newpage

# Appendix
## R Code
``` {r yada, warning = FALSE, message = FALSE}

```

\begin{table}[H]\begin{center}
\caption{{\bf Yada yada}}\label{t:model1}
\begin{tabular}{l|c}
\\
 \hline
Comparison & Tukey p-value  \\ \hline
 \hline
\end{tabular} 
\end{center}
\end{table}

## References

* https://data.cdc.gov/Case-Surveillance/United-States-COVID-19-Cases-and-Deaths-by-State-o/9mfq-cb36
* https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4241048/
* https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3016756/
* https://www.census.gov/data/tables/time-series/demo/popest/2020s-state-total.html#par_textimage
* https://data.cdc.gov/Vaccinations/COVID-19-Vaccinations-in-the-United-States-Jurisdi/unsk-b7fc
* https://healthdata.gov/National/School-Learning-Modalities/aitj-yx37

## Data